Trip Summary ITHIM-R

### 2019-10-11 code/producing_trips_rd/trip-summary.Rmd

```{r, include = FALSE}
source("V:/Group/lambed/ITHIM-R/code/producing_trips_rd/used_functions.R")
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')
```

@@

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/buenos_aires/buenos_aires_trip.csv")
quality_check(trip)
trip_summary$buenos_aires <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/sao_paulo/sao_paulo_trip.csv")
quality_check(trip)
trip_summary$sao_paulo <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/belo_horizonte/belo_horizonte_trip.csv")
quality_check(trip)
trip_summary$belo_horizonte <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/santiago/santiago_trip.csv")
quality_check(trip)
trip_summary$santiago_city <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/bogota/bogota_trip.csv")
quality_check(trip)
trip_summary$bogota_city <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/accra/accra_trip.csv")
quality_check(trip)
trip_summary$accra_city <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/delhi/delhi_trip.csv")
quality_check(trip)
trip_summary$delhi_city <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/bangalore/bangalore_trip.csv")
quality_check(trip)
trip_summary$bangalore_city <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/mexico/mexico_city_trip.csv")
quality_check(trip)
trip_summary$mexico_city <- value

>>>>

```{r, include = FALSE}
source("used_functions.R")
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')
```

@@

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
trip <- read_csv("../../data/local/buenos_aires/buenos_aires_trip.csv")
quality_check(trip)
trip_summary$buenos_aires <- value

trip <- read_csv("../../data/local/sao_paulo/sao_paulo_trip.csv")
quality_check(trip)
trip_summary$sao_paulo <- value

trip <- read_csv("../../data/local/belo_horizonte/belo_horizonte_trip.csv")
quality_check(trip)
trip_summary$belo_horizonte <- value

trip <- read_csv("../../data/local/santiago/santiago_trip.csv")
quality_check(trip)
trip_summary$santiago_city <- value

trip <- read_csv("../../data/local/bogota/bogota_trip.csv")
quality_check(trip)
trip_summary$bogota_city <- value

trip <- read_csv("../../data/local/accra/accra_trip.csv")
quality_check(trip)
trip_summary$accra_city <- value

trip <- read_csv("../../data/local/delhi/delhi_trip.csv")
quality_check(trip)
trip_summary$delhi_city <- value

trip <- read_csv("../../data/local/bangalore/bangalore_trip.csv")
quality_check(trip)
trip_summary$bangalore_city <- value

trip <- read_csv("../../data/local/mexico/mexico_city_trip.csv")
quality_check(trip)
trip_summary$mexico_city <- value
